Paper 1

### 2022-06-14 scripts/Paper 1.Rmd

rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
rainfall.SP$Site <- "SP"

rainfall <- rbind(rainfall_L, rainfall.SP)

@@

@@

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_point(aes(color = Year, size = 2)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

input.daily %>% select(jday, NEE_LT.gC, Year) %>%
  ggplot(., aes(jday, NEE_LT.gC)) +
  geom_line(aes(colour = Year))

```{r cumulative fluxes}

cum.co2fluxes <- input.daily %>%
  ddply(c("Year", "jday", "month"), summarise,
        Fco2 = gofC.f(mean(NEE_LT.gC, na.rm = TRUE)),
        ER = gofC.f(mean(ER_LT.gC, na.rm = TRUE)),
        GPP = gofC.f(mean(GPP_LT.gC, na.rm = TRUE)))

>>>>

rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
rainfall.SP$Site <- "SP"
rainfall <- rbind(rainfall_L, rainfall.SP)

@@

rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
rainfall$month <- as.factor(rainfall$month)

@@

rainfall%>% ddply(c("Year", "season"), summarise,
                    seasonal.sum = sum(Precip, na.rm = TRUE))

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()
```

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))

ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(ER_LT.gC))

Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.mean = mean(Ts.mean))

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic()

GPP.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly GPP")+
  xlab("month")+
  theme_classic()

ER.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()

Ts.summary %>%
  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()
```

```{r cumulative fluxes}
cum.co2fluxes <- input.daily %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month)
```
